%
% rt-labs CLA
%
% For use with SOEM and SOES.
% Enables us to dual license 3rd party contributions. 
%
% Use xelatex to generate PDFs.
%
\documentclass[10pt,a4paper]{letter}

\usepackage{tabularx}
\usepackage{fullpage}
\usepackage{parskip}
\usepackage{indentfirst}
\usepackage[table]{xcolor}
\definecolor{dark-gray}{gray}{0.4}
\definecolor{middle-gray}{gray}{0.7}
\definecolor{light-gray}{gray}{0.95}
\definecolor{rt-green}{RGB}{185,208,52}
\definecolor{light-green}{RGB}{224,231,172}
\usepackage{microtype}
\usepackage{fontspec}
%\usepackage{titlesec}
\setmainfont[Ligatures=TeX]{Lato}
\setsansfont[Ligatures=TeX]{Lato}
\usepackage{graphicx}
\usepackage{float}
\usepackage[yyyymmdd]{datetime}
\usepackage{currfile}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{datatool,filecontents}
\usepackage{enumitem}
\usepackage{spreadtab}
\usepackage{wrapfig}
\usepackage{color}
\usepackage{setspace}
\usepackage{float} % needed to use the H parameter in figure
\setlist[description]{leftmargin=\parindent,labelindent=\parindent}
%\usepackage{fancyhdr}
\usepackage{tabulary}
\usepackage{layout}
%\pagestyle{fancy}
%\renewcommand{\footrulewidth}{0.4pt}%
%\DTLsetseparator{|}
\usepackage{hyperref}

%
% No user serviceable parts below.
%

% Set enumeration to 1, 1.1, and (i)
\renewcommand{\labelenumi} {\arabic{enumi}.} 
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
\renewcommand{\labelenumiii}{(\roman{enumiii})}

\renewcommand{\arraystretch}{2}

\begin{document}

\medskip

\begin{center}
   \Large{\textbf{SOEM/SOES CONTRIBUTOR LICENSE AGREEMENT}}
\end{center}

Thank you for your interest in the SOES and SOEM projects. In order to clarify
the intellectual property license granted with contributions of software from
any person or entity (the "Contributor"), rt-labs AB would like to have
a Contributor License Agreement on file that has been signed by the Contributor,
indicating agreement to the license terms below. This license is for your
protection as a Contributor of software to SOES and SOEM projects and does not
change your right to use your own contributions for any other purpose.

If you have not already done so, please complete this Agreement and send a copy
by regular mail to \textbf{rt-labs AB, Värmlandsgatan 2, SE-413 28 Göteborg,
   Sweden} or by e-mail to \textbf{\texttt{openethercatsociety@rt-labs.com}}.

Please read this document carefully before signing and keep the original for
your records.

%%\begin{Form}
%%\begin{tabularx}{\textwidth}[b]{rX}
%\begin{table}[H]
%\begin{tabular}{ p{3cm} p{10cm} }
%\end{tabular}
%\end{table}
%%\end{tabularx}

%%\end{Form}
\medskip

\begin{enumerate}

   \item You and rt-labs AB hereby accept and agree to the following terms and
      conditions: Your "Contributions" means all of your past, present and
      future contributions of object code, source code and documentation to SOES
      and SOEM projects, however submitted to SOES and SOEM projects, excluding
      any submissions that are conspicuously marked or otherwise designated in
      writing by You as "Not a Contribution."

   \item You hereby grant to rt-labs a non-exclusive, irrevocable, worldwide,
      no-charge, transferable copyright license to use, execute, prepare
      derivative works of, and distribute (internally and externally, in object
      code and, if included in your Contributions, source code form) your
      Contributions. Except for the rights granted to rt-labs in this paragraph,
      You reserve all right, title and interest in and to your Contributions.

   \item You represent that you are legally entitled to grant the above license.
      If your employer(s) have rights to intellectual property that you create,
      you represent that you have received permission to make the Contributions
      on behalf of that employer, or that your employer has waived such rights
      for your Contributions to SOES and SOEM projects.

   \item You represent that, except as disclosed in your Contribution
      submission(s), each of your Contributions is your original creation. You
      represent that your Contribution submissions(s) included complete details
      of any license or other restriction (including, but not limited to,
      related patents and trademarks) associated with any part of your
      Contributions)(including a copy of any applicable license agreement). You
      agree to notify rt-labs of any facts or circumstances of which you become
      aware that would make Your representations in the Agreement inaccurate in
      any respect.

   \item You are not expected to provide support for your Contributions, except
      to the extent you desire to provide support. Your may provide support for
      free, for a fee, or not at all. Your Contributions are provided as-is,
      with all faults, defects and errors, and without any warranty of any kind
      (either express or implied) including, without limitation, any implied
      warranty of merchantability and fitness for a particular purpose and any
      warranty of non-infringement.

\end{enumerate}

\medskip
\begin{Form}
{\renewcommand{\arraystretch}{1.2}%
\begin{tabularx}{\textwidth}[t]{lX}
Full Name & \TextField[name=fullname,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
Email & \TextField[name=email,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
Telephone & \TextField[name=telephone,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
Mailing Address & \TextField[name=address,multiline=true,height=3\baselineskip,donotscroll=true,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
GitHub account & \TextField[name=github,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
Date & \TextField[name=date,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
Please sign & \TextField[name=signature,width=12.5cm,backgroundcolor=light-gray,bordercolor=]{ } \\\cmidrule{2-2}
\end{tabularx}
}
\end{Form}

\end{document}
